---
title: "Master of Business analytics: MBAT"
author: "Patricia Menéndez"
date: 
fontsize: 14pt
output:
  beamer_presentation:
    fig_height: 4.33
    fig_width: 6
    highlight: tango
    keep_tex: no
    incremental: no
    theme: metropolis
    includes:
      in_header: preamble.tex
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE,
  dev.args=list(bg=grey(0.9), pointsize=11))
```

```{r}
library(gridExtra)
library(ggplot2)
library(knitr)
library(tidyverse)


library(lubridate)
library(tsibble)
library(ggwordcloud)

```


## Data is everywhere

\begin{center}
   \includegraphics[height = 7.5cm, width = 8cm]{data-never-sleeps}
\end{center}

## Why Business Analytics?
\begin{itemize}
\item Informed decisions based on facts
\item Facts are measured via data
\item Informed business decisions based on data
\item Business Analytics! 
\end{itemize}

## MBAT
\begin{block}{}
\begin{itemize}
\item Statistical modelling and thinking
\item R
\item Communication and collaboration
end-to-end analytics
\end{itemize}
\end{block}

Learn to solve problems understanding the stats and developing computational methods.

##  Testing

\forestset{
  L1/.style={},
  L2/.style={edge={Orange,line width=2pt}},
  L3/.style={edge={Orange,line width=2pt}},
  L4/.style={edge={Orange,line width=2pt}},
  L5/.style={edge={Orange,line width=2pt}},
}

\begin{forest}
for tree={l sep+=.2cm,s sep+=.15cm,shape=rectangle, rounded corners,
    draw, align=center,
     top color=MonashBlue,  bottom color=MonashBlue}
[\color{white}{Business Analytics}, L1 
  [\color{white}{Informed Decisions based on facts}, L2
    [\color{white}{Facts are measured via data}, L3 
       [\color{white}{Informed decisions need data}, L4]
       [\color{white}{Communicating}, L5]     
    ]
  ]  
]    
\end{forest}

## What does a Business analytics professional do?

\begin{itemize}
\item  Using statistical and computational skills to answer business questions
\item  Visualizing data 
\item  Quantiative odelling (for big and small data \& for simple and complex data) 
\item  Being able to comunicate findings to experts and broad audiences 
\end{itemize}



```{r}

set.seed(43)
data = data.frame(word = c("Data", "Statistics", "Decision making",
                           "R", "Computational statistics", "Modelling",
                           "Visualization", "Comunicating with data", "Business analytics"),
                  weight = c(runif(8, min = 100, max = 800), 900),
                  col = seq(1:9))

set.seed(42)
ggplot(data, aes(label = word, size = weight, color = col)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 24) +
  theme_minimal()

ggsave("figs/word.pdf")
```

## Top jobs under the "4th Industrial revolution"

\begin{columns}
\begin{column}{0.5\textwidth} 
   \begin{block}{}
\begin{enumerate}
\item Data Scientists (19\%)
\item Statistician (33\%)
\item University Professor
\end{enumerate}
\end{block}
\end{column}
\begin{column}{0.5\textwidth}
\begin{center}
   \includegraphics[height = 10cm, width = 10cm]{word}
\end{center}
   
\end{column}
\end{columns}

Data is driving the 4th Industrial Revolution
<!-- \begin{verbatim} -->
<!-- https://www.careercast.com/jobs-rated/best-jobs-of-2019 -->
<!-- \end{verbatim} -->





## Decisions and Data


\begin{center}
   \includegraphics[height = 4.5cm]{data}
\end{center}

\begin{itemize}
\item increasing availability of data in our society
\item Data is used to make decisions
\item Industry, Government, inter-government and NGO
\item Tools for data driven decision making
\end{itemize}



## Companies and governments create stratagies about

\begin{block}{}
\begin{itemize}
\item Relevant data
\item Data Collection
\item Data hiden in my organization?
\item Cleaning and analyzing data
\item Setting up adequate experimental desings
\item Strategies for merging and analytize data
\end{itemize}
\end{block}


## Master of Business Analytics

\begin{itemize}
\item At least one unit of undergraduate statistics.
\item An interest in using data to solve problems and
uncover truths.
\item A combination of mathematics and computing
skills with curiosity about the world.
\item Most likely an undergraduate degree in a
quantitative discipline: engineering, computer
science, mathematics, statistics.
\end{itemize}

## Units --> Advanced Preparatory Studies

\begin{block}{Advanced preparatory studies (24 points)}
\begin{itemize}
\item  ETC5510: Introduction to data analysis
\item  ETC5242: Statistical thinking
\item  ETC5250 Introduction to machine learning
\item  ETC5550 Applied forecasting
\end{itemize}
\end{block}

## Units --> Mastery Knowledge

\begin{block}{Mastery knowledge (48 points)}
\begin{itemize}
\item  ETC5512 Wild-caught data
\item  ETC5513 Collaborative and reproducible practices
\item  ETC5521 Exploratory data analysis
\item  ETC5523 Data story-telling
\item  ETF5500 High dimensional data analysis
\item  ETC5555 Statistical machine learning
\item ETC5580 Advanced statistical modelling
\item  ETC5543 Business analytics creative activity (12) 9
\end{itemize}
\end{block}

## Units --> Application Studies

\begin{block}{Application studies (24 points)}
\begin{itemize}

\item FIT9133 Programming foundations in Python
\item FIT5205 Data in society
\item FIT9132 Introduction to databases
\item MAT9004 Mathematical foundations for data science
\item ETC5410 Bayesian time series econometrics
\item FIT5147 Data exploration and visualisation
\item ETC5555 Statistical machine learning
\item FIT5212 Data analysis for semi-structured data
\end{itemize}
\end{block}

## Job Market

\begin{itemize}
\item Endless job opportunities
\item University
\item Industry
\item Government
\end{itemize}
