---
title: "Master of Business analytics: MBAT"
author: "Patricia Menéndez"
date: 
fontsize: 14pt
output:
  beamer_presentation:
    fig_height: 4.33
    fig_width: 6
    highlight: tango
    keep_tex: no
    incremental: no
    theme: metropolis
    includes:
      in_header: preamble.tex
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE,
  dev.args=list(bg=grey(0.9), pointsize=11))
```

```{r}
library(gridExtra)
library(ggplot2)
library(knitr)
library(tidyverse)


library(lubridate)
library(tsibble)
library(ggwordcloud)

```


## Data is everywhere

\begin{center}
   \includegraphics[height = 7.5cm, width = 8cm]{data-never-sleeps}
\end{center}

## Why Business Analytics?
\begin{itemize}
\item Informed decisions based on facts
\item Facts are measured via data
\item Informed business decisions based on data
\item Business Analytics! 
\end{itemize}


## 

\forestset{
  L1/.style={},
  L2/.style={edge={Orange,line width=2pt}},
  L3/.style={edge={Orange,line width=2pt}},
  L4/.style={edge={Orange,line width=2pt}},
  L5/.style={edge={Orange,line width=2pt}},
}

\begin{forest}
for tree={l sep+=.2cm,s sep+=.15cm,shape=rectangle, rounded corners,
    draw, align=center,
     top color=MonashBlue,  bottom color=MonashBlue}
[\color{white}{Business Analytics}, L1 
  [\color{white}{Informed Decisions based on facts}, L2
    [\color{white}{Facts are measured via data}, L3 
       [\color{white}{Informed decisions need data}, L4]
       [\color{white}{Communicating}, L5]     
    ]
  ]  
]    
\end{forest}

## What does a Business analytics professional do?

\begin{itemize}
\item  Using statistical and computational skills to answer business questions
\item  Visualizing data 
\item  Quantiative odelling (for big and small data \& for simple and complex data) 
\item  Being able to comunicate findings to experts and broad audiences 
\end{itemize}



```{r}

set.seed(43)
data = data.frame(word = c("Data", "Statistics", "Decision making",
                           "R", "Computational statistics", "Modelling",
                           "Visualization", "Comunicating with data", "Business analytics"),
                  weight = c(runif(8, min = 100, max = 800), 900),
                  col = seq(1:9))

set.seed(42)
ggplot(data, aes(label = word, size = weight, color = col)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 24) +
  theme_minimal()

ggsave("figs/word.pdf")
```

## Top jobs under the "4th Industrial revolution"

\begin{columns}
\begin{column}{0.5\textwidth} 
   \begin{block}{}
\begin{enumerate}
\item Data Scientists (19\%)
\item Statistician (33\%)
\item University Professor
\end{enumerate}
\end{block}
\end{column}
\begin{column}{0.5\textwidth}
\begin{center}
   \includegraphics[height = 10cm, width = 10cm]{word}
\end{center}
   
\end{column}
\end{columns}

Data is driving the 4th Industrial Revolution
<!-- \begin{verbatim} -->
<!-- https://www.careercast.com/jobs-rated/best-jobs-of-2019 -->
<!-- \end{verbatim} -->





## Decisions and Data


\begin{center}
   \includegraphics[height = 4.5cm]{data}
\end{center}

\begin{itemize}
\item increasing availability of data in our society
\item Data is used to make decisions
\item Industry, Government, inter-government and NGO
\item Tools for data driven decision making
\end{itemize}



## Companies and governments create stratagies about

\begin{block}{}
\begin{itemize}
\item Relevant data
\item Data Collection
\item Data hiden in my organization?
\item Cleaning and analyzing data
\item Setting up adequate experimental desings
\item Strategies for merging and analytize data
\end{itemize}
\end{block}


## Master of Business Analytics

## Job Market

\begin{itemize}
\item Endless job opportunities
\item University
\item Industry
\item Government
\end{itemize}
