---
title: "Master of Business analytics: MBAT"
author: "Dr Patricia Menéndez, Lecturer MBAT"
date: 
fontsize: 14pt
output:
  beamer_presentation:
    fig_height: 4.33
    fig_width: 6
    highlight: tango
    keep_tex: no
    incremental: no
    theme: metropolis
    includes:
      in_header: preamble.tex
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE,
  dev.args=list(bg=grey(0.9), pointsize=11))
```

```{r}
library(gridExtra)
library(ggplot2)
library(knitr)
library(tidyverse)


library(lubridate)
library(tsibble)
library(ggwordcloud)
library(maps)
library(gapminder)

library(gganimate)

```


```{r , cache = TRUE, eval = FALSE}
#PM Modifications from
#https://gist.github.com/thomasp85/05169ad44ddcc8ed56da6ff7bf7fbe36

anim <- ggplot(gapminder, aes(x = gdpPercap, y=lifeExp, size = 3*pop, colour = country)) +
  geom_point(show.legend = FALSE, alpha = 0.9) +
  scale_color_viridis_d(option ="magma") +
  scale_size(range = c(5, 20)) +
  scale_x_log10() +
  labs(x = "", y = "") +
  theme_void() +
  transition_time(year) +
  shadow_wake(wake_length = 0.15, size = 20,  alpha = FALSE)
anim


anim_save(filename ="figs/animation.png")


```

## Data is collected everywhere and at any time

\begin{columns}
 \begin{column}{0.5\textwidth} 
  \animategraphics[autoplay,loop,height=\textheight]{5}{./figs/animation}{1}{100}
 \end{column}
 \begin{column}{0.5\textwidth}
  \includegraphics[height =6.5cm , width = \textwidth]{data-never-sleeps}
 \end{column}
\end{columns}

\begin{textblock}{10}(0.4,9)
 \fontsize{9}{10}\sf\texttt{https://www.domo.com/learn/data-never-sleeps-7}
\end{textblock}


## Why Business Analytics?
\textbf{Industries and governments need to make:}
\begin{itemize}
 \item[\faPaperPlaneO] Informed decisions based on facts 	\faAreaChart \pause
 \item[\faPaperPlaneO] Facts are measured with data \faDownload \pause
 \item[\faPaperPlaneO] Business analytics experts use statistical and computational
methods to answer business relevant questions using data \faCogs \pause
 \item[\faPaperPlaneO] Business analytic professionals are able to communicate findings
to experts and broad audiences \faComments
\end{itemize}


## Master of Business Analytics --> Starting 2020
\begin{columns}
 \begin{column}{0.5\textwidth} 
 \fontsize{12}{14}
   \begin{block}{}
    \begin{itemize}
     \item[\faArrowRight]  Learn end-to-end analytics including data collection, modeling, collaboration,    communication
     \item[\faArrowRight]  Broad foundation: statistical thinking, probabilistic modeling, computational techniques
     \item[\faArrowRight]  Social conscience, working for a better world
    \end{itemize}
   \end{block}
 \end{column}
 \begin{column}{0.4\textwidth}
  \begin{center}
   \includegraphics[height = 5.5cm, width = 5cm]{hexAustralia}
  \end{center}
 \end{column}
\end{columns}
 
\begin{center}
 Know what you are doing! \textbf{EBS, Monash University}
\end{center}


```{r , fig.width= 10, fig.height=10}

set.seed(43)
data = data.frame(word = c("Data",
                           "Statistics",
                           "Decision making",
                           "R",
                           "Computational statistics",
                           "Modelling",
                           "Visualization",
                           "Comunicating with data",
                           "Business analytics"),
                  weight = c(runif(8, min = 100, max = 800), 900),
                  col = seq(1:9))

set.seed(12)
fig1 = ggplot(data, aes(label = word, size = weight, color = col)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 100) +
  theme_minimal() 

ggsave("figs/word.pdf")
```

## Top jobs under the "4th Industrial revolution"

\begin{columns}
 \begin{column}{0.5\textwidth}
  \includegraphics[width = 6cm, height = 7cm]{word}
 \end{column}
 \begin{column}{0.5\textwidth}
  \begin{block}{}
   \begin{enumerate}
    \item Data Scientists 19\% \faLongArrowUp
    \item Statistician 33\% \faLongArrowUp
    <!-- \item[\faArrowRight] Median salary USD$114K -->
   \end{enumerate}
  \end{block}
 \end{column}
\end{columns}

\textbf{Data is driving the 4th Industrial Revolution}
\begin{textblock}{10}(1, 9)
 \fontsize{9}{10}\sf\texttt{https://www.careercast.com/jobs-rated/best-jobs-of-2019}
\end{textblock}


## Countries looking for MBAT graduates 

\begin{columns}
 \begin{column}{0.5\textwidth} 
  \begin{itemize}
   \item[\faArrowUp] \textbf{Increasing} demand for Business Analytics graduates 
   \item[\faArrowRight] \textbf{Worldwide!}
  \end{itemize}
 \end{column}
 \begin{column}{0.5\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width = 4cm, height = 3.2cm]{worldmap}
  \end{column}
 \end{columns}
\pause
\vspace{0.7cm}
\begin{tcolorbox}
 \faCheck Business analytics professionals are/will play a mayor role in decision making 
 \textbf{with Jobs @}
 \begin{itemize}
  \item Industry
  \item Government
  \item University
  \end{itemize}
 
\end{tcolorbox}

 




```{r , figure = FALSE}
fig2 = ggplot(map_data("world"), aes(long, lat, group=group, fill=region)) + 
  geom_polygon(show.legend = F) +
  theme_bw() +
  ggtitle("Countries looking for business analytics profesionals")

ggsave("figs/worldmap.pdf")
```


## What’s special about MBAT at Monash?
\fontsize{12}{14}\sf
 \begin{itemize}\tightlist
  \item  Taught by internationally renowned researchers. {\color{blue1}{We have authored
  many of the tools that are now taught around the world.}} \pause
  \item Close connections with discipline leaders and primary developers across the globe. \pause
  \item  Cutting edge, focusing on problem solving and hands-on experience.\pause
  \item  Focus on wild data, real problems. {\color{blue1}{We have experience working with industry and government.}}\pause
  \item  Fiercely independent, not sponsored by any software company.\pause
  \item  We only use open-source software for maximum flexibility and accessibility.
 \end{itemize}  

## Monash MBAT is
\begin{tcolorbox}
 \textbf{The only masters course in the world based\\
  entirely around R and taught by leading\\
  R developers.}
\end{tcolorbox}
\fontsize{10.5}{13}\sf
<!-- \includegraphics[]{RStudio-Ball.png} -->
 \begin{columns}
  \begin{column}{0.5\textwidth} 
   \begin{itemize}\tightlist
    \item The \textbf{\color{blue1}{leading statistical programming}} framework.
    \item Completely free and \textbf{\color{blue1}{open-source}}
    \item Used by \textbf{\color{blue1}{every major company in the world}}
    \item Supported by \textbf{\color{blue1}{Microsoft, Google, Facebook, Amazon}}, etc
   \end{itemize}
 \end{column}
 \begin{column}{0.5\textwidth} 
  \begin{block}{}
   \begin{itemize}\tightlist
    \item Rob Hyndman wrote the main forecasting tools.
    \item Di Cook is a member of the R foundation.
    \item The leading R developers visit Monash regularly.
   \end{itemize}
  \end{block}
 \end{column}
\end{columns} 

\begin{textblock}{2.3}(10.5,0)\fontsize{13}{14}\sf
 \includegraphics[width = 2.5cm, height = 2cm]{RStudio-Ball.png}
\end{textblock}


## MBAT users profile

\begin{itemize}
 \item[\faChevronRight] At least \textbf{\color{blue1}{one unit of undergraduate statistics}}.\pause
 \item[\faChevronRight] An \textbf{\color{blue1}{interest}} in using \textbf{\color{blue1}{data}} 
  to solve problems and uncover truths.\pause
 \item[\faChevronRight] A combination of \textbf{\color{blue1}{ curiosity in quantiative  and computational
  methods}} with a \textbf{\color{blue1}{desire}} to make a difference.\pause
 \item[\faChevronRight] An \textbf{\color{blue1}{undergraduate degree}} that has sparked your interest to work 
 with data to answer real life questions.
\end{itemize}

## Units --> \faUniversity \hphantom{} Advanced Preparatory Studies

\begin{block}{Advanced preparatory studies (24 points)}
 \begin{itemize}
  \item  ETC5510: Introduction to data analysis
  \item  ETC5242: Statistical thinking
  \item  ETC5250 Introduction to machine learning
  \item  ETC5550 Applied forecasting
 \end{itemize}
\end{block}

## Units --> \faUniversity \hphantom{} Mastery Knowledge

\begin{block}{Mastery knowledge (48 points)}
 \begin{itemize}
  \item  ETC5512 Wild-caught data
  \item  ETC5513 Collaborative and reproducible practices
  \item  ETC5521 Exploratory data analysis
  \item  ETC5523 Data story-telling
  \item  ETF5500 High dimensional data analysis
  \item  ETC5555 Statistical machine learning
  \item ETC5580 Advanced statistical modelling
  \item  ETC5543 Business analytics creative activity (12)
 \end{itemize}
\end{block}

## Units --> \faUniversity \hphantom{} Application Studies

\begin{block}{Application studies (24 points)}
 \begin{itemize}
  \item FIT9133 Programming foundations in Python
  \item FIT5205 Data in society
  \item FIT9132 Introduction to databases
  \item MAT9004 Mathematical foundations for data science
  \item ETC5410 Bayesian time series econometrics
  \item FIT5147 Data exploration and visualisation
  \item ETC5555 Statistical machine learning
  \item FIT5212 Data analysis for semi-structured data
 \end{itemize}
\end{block}

## MBAT: A World full of opportunities \faGraduationCap


\fontsize{10.5}{13}\sf
 \begin{tcolorbox}
  \begin{itemize}
   \item[\faAngleRight] Highly connected instructors in analytics community
   \item[\faAngleRight] Instructors are active researchers
   \item[\faAngleRight] Learning cutting edge, using latest tools and best established methodology
  \end{itemize}
\end{tcolorbox}
\begin{columns}
 \begin{column}{0.5\textwidth} 
  \begin{itemize}
   \item \textbf{\color{blue1}{Location and duration:}} 1.5 or 2 years full time 
          or 3 or 4 years part time @ Monash Clayton
   \item \textbf{\color{blue1}{Applications}} for our Semester 1 intake (February 2020) are now open.
   \item \textbf{\color{blue1}{Entry requirements:}} Australian bachelor's degree or an equivalent qualification
  \end{itemize}
 \end{column}
\begin{column}{0.5\textwidth}
 \begin{center}
  \textbf{All here \faAt Monash!}
  \includegraphics[height = 4cm, width = 5.5cm]{ana-bg-2-rect}
  \textbf{Jump in!}
  \end{center}
 \end{column}
\end{columns}

 
##

{\placefig{-0.01}{-0.01}{width=1.01\paperwidth,height=\paperheight}{ana-bg-2-rect}
 \begin{textblock}{7.5}(3.5,0.5)\fontsize{24}{30}\sf
  {\color{white}\raggedright\usebeamerfont{title}\par{Many thanks!}}
 \end{textblock}
 \begin{textblock}{3.5}(1.5,3)
  \color{white}\raggedright\usebeamerfont{title}{Questions?}\\[0.2cm]
 \end{textblock}
}

\begin{textblock}{12}(0.7,7.5)
 \color{black}\fontsize{11}{11}\sf\texttt{https://www.monash.edu/business/master-of-business-analytics}
 
\end{textblock}

 




