---
title: "Master of Business analytics: MBAT"
author: "Patricia Menéndez"
date: 
fontsize: 14pt
output:
  beamer_presentation:
    fig_height: 4.33
    fig_width: 6
    highlight: tango
    keep_tex: no
    incremental: no
    theme: metropolis
    includes:
      in_header: preamble.tex
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE,
  dev.args=list(bg=grey(0.9), pointsize=11))
```

```{r}
library(gridExtra)
library(ggplot2)
library(knitr)
library(tidyverse)


library(lubridate)
library(tsibble)
library(ggwordcloud)
library(maps)

```


## Data is everywhere

\begin{center}
   \includegraphics[height =\textheight , width = \textwidth]{data-never-sleeps}
\end{center}

## Why Business Analytics?
\textbf{Industries and governments need to make:}
\begin{itemize}
\item[\faPaperPlaneO] Informed decisions based on facts 	\faAreaChart
\item[\faPaperPlaneO] Facts are measured via data \faDownload
\item[\faPaperPlaneO] Business analytics experts use statistical and computational methods to answer relevant questions using data \faCogs
\item[\faPaperPlaneO] Business analytic profesionals communicate findings to experts and broad audiences \faComments
\end{itemize}


## Master of Business Analytics --> Starting 2020
\begin{columns}
\begin{column}{0.5\textwidth} 

\begin{block}{}
\begin{itemize}
\item[\faArrowRight] Statistical modelling 
\item[\faArrowRight] Computational methods
\item[\faArrowRight] R
\item[\faArrowRight] End-to-end analytics
\item[\faArrowRight] Communicating with data

\end{itemize}
\end{block}

\end{column}
\begin{column}{0.5\textwidth}
\textbf{EBS, Monash University}
\begin{center}
   \includegraphics[height = 5.5cm, width = 6cm]{hexAustralia}
\end{center}
\end{column}
\end{columns}
\begin{center}
Know what you are doing!
\end{center}

<!-- ## Business analytics professional? -->

<!-- \begin{itemize} -->
<!-- \item  Using statistical and computational skills to answer business questions -->
<!-- \item  Visualizing data  -->
<!-- \item  Quantiative modelling  -->
<!-- \item  Comunicating findings to experts and broad audiences  -->
<!-- \end{itemize} -->



```{r , fig.width= 10, fig.height=10}

set.seed(43)
data = data.frame(word = c("Data", "Statistics", "Decision making",
                           "R", "Computational statistics", "Modelling",
                           "Visualization", "Comunicating with data", "Business analytics"),
                  weight = c(runif(8, min = 100, max = 800), 900),
                  col = seq(1:9))

set.seed(12)
fig1 = ggplot(data, aes(label = word, size = weight, color = col)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 100) +
  theme_minimal() 

ggsave("figs/word.pdf")
```

## Top jobs under the "4th Industrial revolution"

\begin{columns}
\begin{column}{0.5\textwidth} 
   \begin{block}{}
\begin{enumerate}
\item Data Scientists (19\%)
\item Statistician (33\%)
\item University Professor
\end{enumerate}
\end{block}
\end{column}
\begin{column}{0.5\textwidth}
\begin{center}
   \includegraphics[width = 6cm, height = 7cm]{word}
\end{center}
   
\end{column}
\end{columns}

\textbf{Data is driving the 4th Industrial Revolution}
<!-- \begin{verbatim} -->
<!-- https://www.careercast.com/jobs-rated/best-jobs-of-2019 -->
<!-- \end{verbatim} -->





## Decisions and Data 



\begin{tcolorbox}
\faCheck Increasing availability of data in our society
\end{tcolorbox}
\begin{tcolorbox}
\faCheck Data is crucial to make decisions 
\end{tcolorbox}
\begin{tcolorbox}
\faCheck Industries and governments make informed decisions based on data
\end{tcolorbox}
\begin{tcolorbox}
\faCheck Business analytics professionals will play a mayor role in decision making 
\end{tcolorbox}





```{r , figure = FALSE}
fig2 = ggplot(map_data("world"), aes(long, lat, group=group, fill=region)) + 
  geom_polygon(show.legend = F) +
  theme_bw() +
  ggtitle("Countries looking for business analytics profesionals")

ggsave("figs/worldmap.pdf")
```



## Worldwide 
Companies and governments are creating stratagies for:

\begin{columns}
\begin{column}{0.5\textwidth} 
\begin{center}
   \includegraphics[height = 8.5cm, width = 6cm]{worldmap}
\end{center}
\end{column}
\begin{column}{0.5\textwidth}

\begin{itemize}
\item Data Collection $\rightarrow$ experimental designs
\item Cleaning and merging data 
\item Analyzing data
\end{itemize}
\end{column}
\end{columns}


## Master of Business Analytics

\begin{itemize}
\item[\faChevronRight] At least \textbf{one unit of undergraduate statistics}.
\item[\faChevronRight] An \textbf{interest} in using \textbf{data} to solve problems and
uncover truths.
\item[\faChevronRight] A combination of \textbf{mathematics and computing
skills} with \textbf{curiosity} about the world.
\item[\faChevronRight] Most \textbf{likely} an \textbf{undergraduate degree} in a
quantitative discipline: \textbf{engineering, computer
science, mathematics, statistics}.
\end{itemize}

## Units --> \faUniversity Advanced Preparatory Studies

\begin{block}{Advanced preparatory studies (24 points)}
\begin{itemize}
\item  ETC5510: Introduction to data analysis
\item  ETC5242: Statistical thinking
\item  ETC5250 Introduction to machine learning
\item  ETC5550 Applied forecasting
\end{itemize}
\end{block}

## Units --> \faUniversity Mastery Knowledge

\begin{block}{Mastery knowledge (48 points)}
\begin{itemize}
\item  ETC5512 Wild-caught data
\item  ETC5513 Collaborative and reproducible practices
\item  ETC5521 Exploratory data analysis
\item  ETC5523 Data story-telling
\item  ETF5500 High dimensional data analysis
\item  ETC5555 Statistical machine learning
\item ETC5580 Advanced statistical modelling
\item  ETC5543 Business analytics creative activity (12) 9
\end{itemize}
\end{block}

## Units --> \faUniversity Application Studies

\begin{block}{Application studies (24 points)}
\begin{itemize}

\item FIT9133 Programming foundations in Python
\item FIT5205 Data in society
\item FIT9132 Introduction to databases
\item MAT9004 Mathematical foundations for data science
\item ETC5410 Bayesian time series econometrics
\item FIT5147 Data exploration and visualisation
\item ETC5555 Statistical machine learning
\item FIT5212 Data analysis for semi-structured data
\end{itemize}
\end{block}

## MBAT: A World full of opportunities \faGraduationCap


\begin{center}
\textbf{All here \faAt Monash!}

   \includegraphics[height = 8.5cm, width = 6cm]{earth_NASA}
   
   \textbf{Jump in!}
\end{center}



